---
title: "Compute image texture metrics"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The following example shows how to compute image texture metrics from Landsat 8 
data downloaded from the [USGS Earth Explorer](http://earthexplorer.usgs.gov/).


## Reading Landast 8 data

We will use the test data set supplied with this package. In order to read the
data set, just supply the filename (or list of filenames) to the `satellite()`
function.

```{r}
library(satellite)
path <- system.file("extdata", package = "satellite")
files <- list.files(path, pattern = glob2rx("LC8*.TIF"), full.names = TRUE)
sat <- satellite(files)
```


## Calculate image metrics

Image metrics will be calculated using wrapper functions for the glcm package
developed by Alex Zvoleff.
```{r}
imageTextures(sat, bcde = "B003n", window = c(5,5), statistics = "mean")
```
